---
title: "Data-Scientific Programming: Assignment 1"
author: "Akhmed Malsagov"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```


### Directions: Refer to [sections 3.1-3.6 in R for Data Science](https://r4ds.had.co.nz/data-visualisation.html), and the Class Notes.

We'll start by loading the tidyverse package. 

```{r}
library(tidyverse)
```

In this assignment, we will use the `mpg` dataset, referenced in the book. This dataset is automatically loaded with the `tidyverse` package. 

## Question 1 

### Create a scatterplot for the `mpg` dataset. Display `displ` on the x-axis and `hwy` on the y-axis. Add color to represent type of drive (`drv`), and size to represent the number of cylinders (`cyl`).

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = drv, size = cyl))
```


## Question 2

### Modify the plot from question 1 to place the variable `class` (representing type of car) on the x-axis. Explain why a scatterplot is not an appropriate way to graph these data.   

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = hwy, color = drv, size = cyl))
```

Type explanation here. 
Because some of the classes can use the same size of the engine, and it wouldn't show us the real picture of how fuel efficiancy changes between class of cars.

## Question 3

### Fix the code below so that the points are actually blue. 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue"))
```

## Question 4

### Now change the code from question 3 to color the points based on whether the car was released before 2004. Hint(see Exercise 3.3.1: question 6). 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue", color = year < 2004))
```


